Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-06-07 manuscript.Rmd
predictors

```{r null models}
df_list <- list(df_personality,
                df_affect,
                df_thought)

null_models <- df_list %>% 
  map_dfr(
    ~ lmer(judgment ~ (1|perceiver_id) + 
             (1|target_id) + 
             (1|dyad_id),
           data = .x) %>% 
      broom.mixed::tidy()
    )

@@

```{r}
df_thought_long <- 
  df_thought %>% 
  pivot_longer(cols = InsecAtt_c:rapport_c,
               names_to = "vars",
               values_to = "value")

df_thought_long <- split(df_thought2, df_thought2$vars)

models5 <- map_dfr(df_thought5, ~
            lmer(judgment ~ value +
             (1 | perceiver_id) + 
             (1 | target_id) +
             (1 | dyad_id),
           data = .x) %>% 
             broom.mixed::tidy() %>% 
             suppressWarnings(), 
           .id = "Predictors"
           )

df_thought5 <- 
  df_thought5 %>% 
  mutate(m1 = map(data, ~
            lmer(judgment ~ value +
             (1 | perceiver_id) + 
             (1 | target_id) +
             (1 | dyad_id),
           data = .x)
                 )
         )

df_thought3 <- 
  df_thought %>% 
  pivot_longer(cols = InsecAtt_c:rapport_c,
               names_to = "vars",
               values_to = "value") %>% 
  group_by(vars) %>% 
  nest()

df_thought3 <- 
  df_thought3 %>% 
  mutate(m1 = map(data, ~
            lmer(judgment ~ value +
             (1 | perceiver_id) + 
             (1 | target_id) +
             (1 | dyad_id),
           data = .x)
                 )
         )

>>>>

### create a list
df_list <- list(df_personality,
                df_affect,
                df_thought)

bind_rows(df_list, .id = "Domain") %>% 
  mutate(Domain = recode(Domain, 
                         "1" = "Personality",
                         "2" = "Affect",
                         "3" = "Thought")
         ) %>% 
  group_by(Domain) %>% 
  nest() %>% 
  drop_na() %>% 
  mutate(N = map_dbl(data, nrow)
         ) %>% 
  select(-data) %>% 
  kable_style(title = "<center><b>Number of Total Observations across Domains</b></center>")
```

```{r null models}
null_models <- df_list %>% 
  map_dfr(
    ~ lmer(judgment ~ (1|perceiver_id) + 
             (1|target_id) + 
             (1|dyad_id),
           data = .x) %>% 
      broom.mixed::tidy()
    )

@@

```{r, include = FALSE}
# I tried to combine everything in a single loop creating double-nested data but failed miserably

# personality 
df_personality_long <- 
  df_personality %>% 
  pivot_longer(cols = InsecAtt_c:rapport_c,
               names_to = "vars",
               values_to = "value")

df_personality_long <- split(df_personality_long, df_personality_long$vars)

preds_pers <- map_dfr(df_personality_long, ~
            lmer(judgment ~ value + self_norm:value + self_dist:value +
                       (1 | perceiver_id) +
                       (1 | target_id) +
                       (1 | dyad_id),                   
                     data = .x) %>% 
             broom.mixed::tidy() %>% 
             suppressWarnings() %>% 
             suppressMessages(), 
           .id = "Predictors"
           )

# affect
df_affect_long <- 
  df_affect %>% 
  pivot_longer(cols = InsecAtt_c:rapport_c,
               names_to = "vars",
               values_to = "value")

df_affect_long <- split(df_affect_long, df_affect_long$vars)

preds_aff <- map_dfr(df_affect_long, ~
            lmer(judgment ~ value + norm:value + distinct:value +
                       (1 | perceiver_id) +
                       (1 | target_id) +
                       (1 | dyad_id),                   
                     data = .x) %>% 
             broom.mixed::tidy() %>% 
             suppressWarnings() %>% 
             suppressMessages(), 
           .id = "Predictors"
           )

# thought
df_thought_long <- 
  df_thought %>% 
  rename(Normative = BaselineEA100,
         Distinctive = CrrctdEAnoneg) %>% 
  pivot_longer(cols = InsecAtt_c:rapport_c,
               names_to = "vars",
               values_to = "value")

df_thought_long <- split(df_thought_long, df_thought_long$vars)

preds_thou_norm <- map_dfr(df_thought_long, ~
            lmer(Normative ~ value +
                       (1 | perceiver_id),
                     data = .x) %>% 
             broom.mixed::tidy() %>% 
             suppressWarnings(), 
           .id = "Predictors"
           )

preds_thou_dist <- map_dfr(df_thought_long, ~
            lmer(Distinctive ~ value +
                       (1 | perceiver_id) + 
                       (1 | target_id) +
                       (1 | dyad_id),
                     data = .x) %>% 
             broom.mixed::tidy() %>% 
             suppressWarnings(), 
           .id = "Predictors"
           )
# table 4
tabl4 <- bind_rows(
  preds_pers,
  preds_aff,
  preds_thou_norm,
  preds_thou_dist,
  .id = "Domain"
) %>% 
  mutate(across(estimate:df, round, 2),
         p.value = scales::pvalue(p.value)
         )
```

```{r}
tabl4 %>% 
  select(-Domain) %>% 
  kable_style(title = "<center><b>Predictors of Interpersonal Accuracy</b></center>") %>% 
  kableExtra::pack_rows("Personality", 1, 208) %>% 
  kableExtra::pack_rows("Affect", 209, 416) %>% 
  kableExtra::pack_rows("Normative Thought", 417, 520) %>% 
  kableExtra::pack_rows("Distinctive Thought", 521, 676) %>% 
  kableExtra::scroll_box(height = "1000px")
```
